---
title: 'Week 4 Part 1: Confidence Intervals and T-tests'
author: "Shelby Smith"
date: "11/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Confidence Intervals

Mean and confidence interval are meaningful
p-value isn't meaningful here because default NULL= otter length is 0in 

```{r}
otter_length<- c(38,41,50,27,32,41,48,60,43)

t.test(otter_length)
```

## T-test (1-sample)

?t.test looks up a function

See a clain: mean otter length is 50 inches. 
I'm going to use my sample for otters to test this claim. 

```{r}
otter_test<- t.test(x=otter_length, mu=50)
otter_test
```
If the population mean is really 50 inches, there is a 4.44% change that I chose a random sample from that population that has a mean at least as far as 50 as my mean. 

## Two-sample T-test

First use histogram or QQplot 

```{r}
desert_bighorns<- c(34, 45, 56, 67, 23, 43, 12, 32)
sierra_bighorns<- c(23,43,21,11,12,12,13,15)

t.test(x=desert_bighorns, y=sierra_bighorns)
```
Mean of Desert Bighorns 39
Mean of Sierra Bighorns 18.75
confidence interval usually not reported here 
Null hypotheses- true difference in means is not equal to 0
p-value: 1% lots of evidence that these were drawn from different populations 
low chance that these samples were drawn from a population with the same mean 
